MADA Project: COVID-19 Vaccinations and recovery

### 2021-11-29 products/manuscript/Manuscript.Rmd
MADA project part 5 (with references)

The next analysis was creating a machine learning modeling technique called the LASSO model. This type of modeling will create multiple models from a five-fold cross-validation and a tuning grid which will try to find the best performing model. From the LASSO we find that model 25 give the best model.

**Need to find a way to extract this model**

@@

## General Background Information
COVID-19 hit the world by storm and is a possible ever-lasting change to the way society acts. It also had an impact on each countries funding towards health care. Actions within the past two years have been taken to help fight against this virus. Although COVID-19 has been here for over two year, there is still problems with under staffing in hospitals and not enough beds at some hospitals. Recovery rates are still high in the United States but what about the whole world. Other countries are still getting hit hard by this virus. In terms of vaccination output, there has been recent back and forth movements on people getting the vaccination. Although in developed countries this happens but what about the less developed countries and regions such as Africa. While people in the United States are fighting about whether the vaccine should be given or not, the people in these other countries might have a limited supply.

Looking at the difference in recovered patients and those who have died will be beneficial in determining if more care is needed in certain countries. I also think the percentage of people vaccinated is also affected and can lead to important results that might show we need more either distribution or requirements of the vaccines.

@@

<\ br>

@@

_Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end_

>>>>

The next analysis was creating a machine learning modeling technique called the LASSO model. This type of modeling will create multiple models from a five-fold cross-validation and a tuning grid which will try to find the best performing model. From the LASSO we find that model 27 give the best model, and the amount of cases, which continent the country resides in, and the type of government have impacts to the vaccination proportions. Compared to Africa, South America and Asia increases the proportion of vaccinations the most while an increase of cases means more vaccinations as well. A monarchy government compared to a republic government has more people vaccinated proportionally.

@@

## General Background Information
COVID-19 hit the world by storm and is a possible ever-lasting change to the way society acts. It also had an impact on each countries funding towards health care. Actions within the past two years have been taken to help fight against this virus. Although COVID-19 has been here for over two year, there is still problems with under staffing in hospitals and not enough beds at some hospitals. Recovery rates are still high in the United States but what about the whole world. Other countries are still getting hit hard by this virus. In terms of vaccination output, there has been back and forth movements on people getting the vaccination. A poll was close to when vaccinations were starting to disperse where only 51% of adults in the United States said they would get a vaccine [@choi21]. Although in developed countries this happens but what about the less developed countries and regions such as Africa. While people in the United States are fighting about whether the vaccine should be given or not, the people in these other countries might have a limited supply. According to the United Nations in September, there is still an unequal amount of vaccinations going to developed and less developed countries. This could be due to the cost of each vaccination [@UN21]. In a paper by Choi, as of January 2021, cases were fairly even between developed and less developed countries [@choi21]. This just shows that although COVID-19 is affected everyone, the supply is not equal between all countries even though all countries need it.

Looking at the difference in recovered patients and those who have died will be beneficial in determining if more care is needed in certain countries. According to  paper by Liang et al, the mortality rates were negatively impacted by the number of tests performed and also based on the countries economic status and government [@liang20]. I also think the percentage of people vaccinated is also affected and can lead to important results that might show we need more either distribution or requirements of the vaccines.

@@

@@
